A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-22 graph_syntax.tex
define t_{edge} and t_{node} functions

\subsection{Node and Edge Types}
  \label{ss:types}
  We now define different types of nodes and edges with specific properties to compose graphs used to represent an MDAO problem. 
  There are three node types:  
  \begin{description}
    \item[variable:] represents scalar or array data
    \begin{equation} 
      V_{\txt{var}} = \{v \st t_{\txt{node}}(v) = \txt{`variable'}\}
    \end{equation}

@@

  In addition to the three node types, there are two edge types:

>>>>

\subsection{Node and Edge Types}
  \label{ss:types}
  To distinguish between different kinds of nodes, we define the function 
  $t_{\txt{node}}(v)$ which returns one of three different types of nodes:

  \begin{description}
    \item[variable:] represents scalar or array data
    \begin{equation} 
      V_{\txt{var}} = \{v \st t_{\txt{node}}(v) = \txt{`variable'}\}
    \end{equation}

@@

  In addition we define the function $t_{\txt{edge}}(e)$ which returns one of 
  two different types of edges:
